### 2014-05-21 Docs/visualization/visualization.tex

{\tt AmrPostprocessing/python} provides some simple commandline
tools for doing visualizations of \boxlib\ plotfiles.  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

@@

>>>>

{\tt AmrPostprocessing/python} provides some simple commandline
tools for doing visualizations of \boxlib\ plotfiles (note: a subset
of these are distributed directly with \boxlib\ in {\tt BoxLib/Tools/Py\_util/}).  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

@@

Some sample scripts that use \yt\ with \maestro\ data are contained in 
{\tt MAESTRO/Util/yt/}.
